...

### 2023-09-16 manuscript/01_main.Rmd
updated rmd structure to bookdown2

---
title: 
author: "Karthik Thrikkadeeri"
date: "28/11/2021"
bibliography: msc-thesis.bib
output: 
  word_document:
    reference_docx: rmd_word_template.docx
    number_sections: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

# Abstract

The general effects of canopy cover can be separated into those of heterogeneity---which might affect birds through light conditions---and those of absolute densities---which might indirectly affect other aspects of the habitat such as tree girth.

@@

# Bibliography

>>>>

# Abstract {.unnumbered}

TBD

<!-- The general effects of canopy cover can be separated into those of heterogeneity---which might affect birds through light conditions---and those of absolute densities---which might indirectly affect other aspects of the habitat such as tree girth. -->

# Keywords {.unnumbered}

TBD

\newpage

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

# References

::: {#refs}
:::

\newpage

@@
